%% UNCOMMENT these lines below (and remove the 2 commands above) if you want to embed the bibliografy.
\begin{thebibliography}{00}
    \bibitem{b1} A. M. Priyatno, L. S. Tanjung, W. F. Ramadhan, P. Cholidhazia, P. Z. Jati, and F. I. Firmananda, "Comparison Random Forest Regression and Linear Regression For Forecasting BBCA Stock Price," \textit{Jurnal Teknik Industri Terintegrasi}, vol. 6, no. 3, pp. 718-732, Jul. 2023.
    \bibitem{b2} M. Ridwan, K. Sadik, and F. M. Afendi, "Comparison of ARIMA and GRU Models for High-Frequency Time Series Forecasting," \textit{Scientific Journal of Informatics}, vol. 10, no. 3, pp. 389–400, Jan. 2024.
    \bibitem{b3} S. Zaheer et al., "A Multi Parameter Forecasting for Stock Time Series Data Using LSTM and Deep Learning Model," vol. 11, no. 3, p. 590, Jan. 2023.
    \bibitem{b4} P. Mondal, L. Shit, and S. Goswami, "Study of Effectiveness of Time Series Modeling (Arima) in Forecasting Stock Prices," \textit{International Journal of Computer Science, Engineering and Applications}, vol. 4, no. 2, p. 13, Apr. 2014.
    \bibitem{b5} S.-H. Chang et al., "Short-Term Stock Price-Trend Prediction Using Meta-Learning," in \textit{IEEE International Conference on Systems, Man and Cybernetics}, 2021, doi: 10.48550/arXiv.2105.13599.
    \bibitem{b6} H. Hewamalage, C. Bergmeir, and K. Bandara, "Recurrent Neural Networks for Time Series Forecasting: Current Status and Future Directions," Faculty of Information Technology, Monash University, Melbourne, Australia, arXiv:1909.00590v5 [cs.LG], Dec. 23, 2020.
    \bibitem{b7} B. N. Oreshkin, N. Chapados, D. Carpov, and Y. Bengio, "N-BEATS: Neural Basis Expansion Analysis for Interpretable Time Series Forecasting," arXiv:1905.10437v4 [cs.LG], Feb. 20, 2020.
    \bibitem{b8} C. Challu, K. G. Olivares, B. N. Oreshkin, F. Garza, M. Mergenthaler-Canseco, A. Dubrawski, "N-HiTS: Neural Hierarchical Interpolation for Time Series Forecasting," arXiv:2201.12886v6 [cs.LG], Nov. 29, 2022.
    % VARMA
    \bibitem{varma_1} Prakhar Prasad, "Time Series - VARMA," [Online], Available: \href{https://www.kaggle.com/code/prakharprasad/time-series-varma}{https://www.kaggle.com/code/prakharprasad/time-series-varma}.
    \bibitem{varma_2} A. H. Al-Nasser and L. T. Abdullah, "The Estimators of Vector Autoregressive Moving Average Model VARMA of Lower Order: VARMA (0,1), ARMA (1,0), VARMA (1,1), VARMA (1,2), VARMA (2,1), VARMA (2,2) with Forecasting," \textit{Iraqi Academics Syndicate International Conference for Pure and Applied Sciences, Journal of Physics: Conference Series}, vol. 1818, p. 012145, 2021. doi: 10.1088/1742-6596/1818/1/012145.
    \bibitem{varma_3} Michael Fuchs, "Time Series Analysis - Regression Extension Techniques for Multivariate Time Series," [Online], Available: \href{https://michael-fuchs-python.netlify.app/2020/10/29/time-series-analysis-regression-extension-techniques-for-forecasting-multivariate-variables/#varma}{https://michael-fuchs-python.netlify.app/2020/10/29/time-series-analysis-regression-extension-techniques-for-forecasting-multivariate-variables/\#varma}.

    % RNN
    \bibitem{rnn_1} sabankara, "Recurrent Neural Networks for Time Series," May 25, 2023, [Online]. Available: \href{https://sabankara.medium.com/recurrent-neural-networks-for-time-series-b3132a6afb6a}{https://sabankara.medium.com/recurrent-neural-networks-for-time-series-b3132a6afb6a}.
    \bibitem{rnn_2} Afshine Amidi and Shervine Amidi, "Recurrent Neural Networks cheatsheet," [Online]. Available: \href{https://sabankara.medium.com/recurrent-neural-networks-for-time-series-b3132a6afb6a}{https://sabankara.medium.com/recurrent-neural-networks-for-time-series-b3132a6afb6a}.

    % NBeats
    \bibitem{nbeats_1} Yuqiang Pan, "Data label for time series mining (Part 4) Interpretability Decomposition Using Label Data," [Online]. Available: \href{https://www.mql5.com/en/articles/13218}{https://www.mql5.com/en/articles/13218}.
    \bibitem{nbeats_2} Daniel Bourke, "Using the N-BEATS algorithm to predict the price of Bitcoin (time series with TensorFlow)," [Online Video], Available: \href{https://www.youtube.com/watch?v=pUUhQyUEZSk}{https://www.youtube.com/watch?v=pUUhQyUEZSk}.
    \bibitem{nbeats_3} Daniel Bourke, "Milestone Project 3: Time series forecasting in TensorFlow (BitPredict)," [Online], Available: \href{https://github.com/mrdbourke/tensorflow-deep-learning/blob/main/10_time_series_forecasting_in_tensorflow.ipynb}{https://github.com/mrdbourke/tensorflow-deep-learning/blob/main/10\_time\_series\_forecasting\_in\_tensorflow.ipynb}.

    % N-HiTS
    \bibitem{nhits_1} Cristian Challu, "NHITS Long-Horizon Forecast," [Online], Available: \href{https://github.com/Nixtla/neuralforecast/blob/main/nbs/examples/LongHorizon_with_NHITS.ipynb}{https://github.com/Nixtla/neuralforecast/blob/main/nbs/examples/\\LongHorizon\_with\_NHITS.ipynb}.
    \bibitem{nhits_2} Nixtla, "Neuralforcast NHITS and AutoNHITS," [Online], Available: \href{https://github.com/Nixtla/neuralforecast}{https://github.com/Nixtla/neuralforecast}.
    \bibitem{nhits_3} Jonte Dancker, "N-HiTS — Making Deep Learning for Time Series Forecasting More Efficient," May 31, 2024, [Online]. Available: \href{https://towardsdatascience.com/n-hits-making-deep-learning-for-time-series-forecasting-more-efficient-d00956fc3e93}{https://towardsdatascience.com/n-hits-making-deep-learning-for-time-series-forecasting-more-efficient-d00956fc3e93}.

\end{thebibliography}
%%%%%%%%%%%%%%%